---
title: "MSNA 2019"
author: "BGD GIS DATA UNIT"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: true
---

```{r setup, include=FALSE, warning = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning = FALSE)

population<-c("Host","Refugee")[2]
write_output<-c("yes","no")[1]



library(dplyr)
library(stringr)
library(ggplot2)
library(lubridate)
library(rgdal)
library(HighFrequencyChecks)
library(kableExtra)
library(gsubfn)
library(stringi)
library(sf)
library(data.table)
source("Functions/GIS_Project_Functions.R")
source("Functions/Load_Audit.R")
source("Functions/get_na_response_rates.R")
source("Functions/ActivatePaths.R")




zip_download_info <- fileSnapshot(audit_zip_dir)
audit_zipfile<-paste0(audit_zip_dir,"/", rownames(zip_download_info$info[which.max(zip_download_info$info$mtime),]))

#LOAD IN GIS DATA
boundary_gdb<- "Inputs/GIS"
unions<-readOGR(boundary_gdb,"BGD_Teknaf_Ukhia_Unions")
camp_blocks<-readOGR(boundary_gdb,"190310_Outline_Rohingya_Refugee_CampBlock_A2")
camp_blocks<-spTransform(camp_blocks,CRS(proj4string(unions)))

mahjee_blocks<-readOGR(boundary_gdb,"NPM-R14-SA_20190312")

strata_spatial<-readOGR(boundary_gdb,"190310_Outline_Rohingya_Refugee_Camp_A1")


HH<-read.csv(HH_path, stringsAsFactors = FALSE, na.strings=c("", " ", NA))
Indiv<-read.csv(Indiv_path, stringsAsFactors = FALSE, na.strings=c("", " ", NA))
SampleSize<- read.csv(samples_required_data_path, stringsAsFactors = FALSE,na.strings=c("", " ", NA))


  
#REQUIRED ONLY THE FIRST DAY OF DATA COLLECTION
############################################################
# HH$reported_date<-Sys.Date()
# todays_date_log<- HH %>% select(X_index, reported_date)
# write.csv(todays_date_log,date_log_path, row.names=FALSE)
#############################################################
date_log<-read.csv(date_log_path, stringsAsFactors = FALSE, 
                   na.strings = c("", " ", NA))


# date_log$reported_date <-dmy(date_log$reported_date )
date_log$reported_date <-ymd(date_log$reported_date )

HH<-HH %>% dplyr::left_join(date_log, by= "X_index") 
HH<-HH %>% 
  mutate(
    reported_date=if_else(is.na(reported_date), Sys.Date(), reported_date)
  ) 

date_log_full<- HH %>% select(X_index,reported_date)



#CORRECT SPATIAL ATTRIBUTES
########################################################################

long_lat<-c("X_gps_reading_longitude","X_gps_reading_latitude")
#REMOVE SENSITIVE DATA (GPS) AND CORRECT UNIONS TO BOUNDARIES?

HH_spatial<-HH
coordinates(HH_spatial)<-long_lat
proj4string(HH_spatial)<-proj4string(unions)

if( population=="Host"){
  HH_corrected_spatial<-spatial_join(HH_spatial, unions)
  HH_corrected_spatial_df<- data.frame(coordinates(HH_corrected_spatial),HH_corrected_spatial@data)
  HH_Desensitized<-HH_corrected_spatial_df %>% select(-contains("gps")) %>% select(-(adm2_en:lab_rot))
}
#WILL NEED TO FIX GHIS ONCE WE GET SOME MORE DATA
##########################################################################
if(population=="Refugee"){
  HH_corrected_spatial<-spatial_join(HH_spatial, strata_spatial)
  HH_corrected_spatial_df<- data.frame(coordinates(HH_corrected_spatial),HH_corrected_spatial@data)
  HH_referrals_cmp_block<- spatial_join(HH_corrected_spatial[!is.na(HH_corrected_spatial$referral_ID),], camp_blocks)
  referrals_block_and_mahj<-spatial_join(HH_referrals_cmp_block, mahjee_blocks)
  referrals_desensitized<- referrals_block_and_mahj@data %>% 
    select(-contains("gps")) %>% 
    select(X_uuid,
           reported_date,
           enumerator_id,
           starts_with("referral"), 
           camp_id= New_Camp_N,
           iscg_block_id=Block_ID,
           mahjee_block_id=LocalBlock
           )
  HH_Desensitized<-HH_corrected_spatial_df %>% select(-contains("gps")) %>% select(-(Name_Alias:X_count))

}

#WRITE DESENSITIZED DATA TO DROPBOX



HH_yes_consent<- HH_corrected_spatial_df %>% filter(informed_consent== "yes")
HH_today_yes_consent<-HH_yes_consent %>% filter(reported_date==Sys.Date())
HH_new<-HH_corrected_spatial_df

Indiv_yes_consent<- Indiv %>% filter(X_submission__uuid %in% HH_yes_consent$X_uuid)


consent<- "informed_consent"
mindur<-26 #change to 26 from 35



```

# `r ifelse(population=="Host","Host Community", "Refugees")`

##GIS CHECKS


Points > **`r buffer`** meters away from the random sample points

```{r}


if(population=="Host"){
reportcol2<-c("enumerator_id","X_uuid", "union_name")
}
if(population=="Refugee"){
  reportcol2<-c("enumerator_id","X_uuid", "New_Camp_N")
}
#NEED GSUBFN PACKAGE
# list[dts,err]<-chk1dii_GIS_Xm(target_points, HH, long_lat, buffer, consent, reportcol2, TRUE)
list[dataset,outside_buffer]<-chk1dii_GIS_Xm(target_points, HH_corrected_spatial_df, long_lat, buffer, consent, reportcol2, TRUE)
#get distance to closest poitn

#measure distance between poitns
################################################
HH_sf<-st_as_sf(HH_corrected_spatial)
target_sf<-st_as_sf(target_points)
# FOR DISTANCE CALCULATION
###########################################################
dist_list<-list()
for(i in seq_len(nrow(HH_sf))){
    closest <- target_sf[which.min(
    st_distance(target_sf, HH_sf[i,])),]
    dist_list[[i]]<-data.frame(X_uuid=HH_sf[i, "X_uuid"],dist=st_distance( HH_sf[i,], closest), target_name= closest$Name)
}
dist_df<-do.call("rbind", dist_list)

outside_buffer<-outside_buffer %>%
  left_join(dist_df %>% as.data.frame(), by=c("X_uuid"= "X_uuid.X_uuid" )) %>% select(-X_uuid.geometry)

outside_buffer<-chk1dii_GIS_Xm(target_points, HH_corrected_spatial_df, long_lat, buffer, consent, reportcol2, TRUE)[2]
############

 outside_buffer %>% kable( longtable = T, booktabs = T, linesep = "",caption= "Problematic Points Based on Location") %>% kable_styling(position = "center")
# kable(outside_buffer, "latex", longtable = T, booktabs = T, linesep = "", caption= "Problematic Points Based on Location") %>% kable_styling(position = "center")
```

## TRACKING 

```{r eval=TRUE, echo=FALSE, results='asis'}

if(population=="Refugee"){
tracking_sheet<-HighFrequencyChecks::chk7bii_tracking(ds=dataset,
                                      sf =SampleSize,dssite =strata,sfsite = sf_strata,
                                      survcons = "informed_consent",sftarget = "points_needed",
                                      sfnbpts ="points_w_buffer_needed",
                                      formul =
                                        c("done-no-not_eligible-child_head-no_one","done-no-not_eligible-child_head-no_one-points_needed"),
                                colorder=c("site","points_needed","points_w_buffer_needed","done","not_eligible", "child_head","no","yes","final","variance"))}

if(population=="Host"){
tracking_sheet<-HighFrequencyChecks::chk7bii_tracking(ds=dataset,
                                      sf =SampleSize,dssite =strata,sfsite = sf_strata,
                                      survcons = "informed_consent",sftarget = "points_needed",
                                      sfnbpts ="points_w_buffer_needed",
                                      formul =
                                        c("done-no-not_eligible","done-no-not_eligible-points_needed"),
                                colorder=c("site","points_needed","points_w_buffer_needed","done","not_eligible", "deleted","no","yes","final","variance"))}


simplified_tracking_table<-HH_corrected_spatial_df %>% 
  group_by_({strata}) %>% 
  summarise(
    number_yes= sum(informed_consent=="yes"),
    number_not_yes= sum(informed_consent!="yes")
  ) %>% 
  
  right_join(SampleSize, by= setNames(sf_strata,strata)) %>% 
  mutate(points_remaining= points_needed-number_yes) %>% 
  select({strata},points_needed, points_w_buffer_needed, number_yes,number_not_yes,points_remaining)




simplified_tracking_table%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Simplified Tracking Sheet (no data checks/deletions)") %>% kable_styling(position = "center")


tracking_sheet%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Tracking Sheet") %>% kable_styling(position = "center")
# kable(tracking_sheet, "latex", longtable = T, booktabs = T, linesep = "", caption= "Tracking Sheet") %>% kable_styling(position = "center")
#IF NOT ALL THREE TYPES OF EDITED CONSENT ARE AVAILABLE
##################################################################################################################################
# dataset$adm4_en
# tracking_sheet<-HighFrequencyChecks::chk7bii_tracking(ds=HH_corrected_spatial_df,
#                                       sf =SampleSize,dssite ="adm4_en",sfsite = "Union",
#                                       survcons = "informed_consent",sftarget = "points_needed",
#                                       sfnbpts ="points_w_buffer_needed",
#                                       formul =c("done-no-not_eligible-deleted","done-no-not_eligible-deleted-points_needed"),
#                                 colorder=c("site","points_needed","points_w_buffer_needed","done","not_eligible","no","yes","final","variance"))

######################################################################3
# wil be a problem if there is not all the consent options in the data set.
# formul = c("done-no-not_eligible-deleted","done-no-not_eligible-deleted-points_needed"),
# colorder=c("site","points_needed","points_w_buffer_needed","done","not_eligible","no","yes","final","variance", "deleted"))

```

## Outliers
### Expenditures 

```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}
if(population=="Refugee"){
  low_bound<-2
  low_bound_label<-"2 or less"
  high_bound<-14
  high_bound_label<-"over 14"
}
if(population=="Host"){
  low_bound<-4
  low_bound_label<- "4 or less"
  high_bound<-13
  high_bound_label<-"over 13"
}


expenditure_cols<-HH_yes_consent %>%
  filter() %>% select(starts_with("exp")) %>% colnames() 


HH_yes_consent[,expenditure_cols]<-sapply(HH_yes_consent[,expenditure_cols], function(x) ifelse(is.na(x),"0_bdt",x)) %>% data.frame()
HH_yes_consent[,expenditure_cols]<-sapply(HH_yes_consent[,expenditure_cols], function(x) ifelse(x=="0_bdt", 0, 1)) %>% data.frame()

Expenditure_outliers<-HH_yes_consent %>%
  mutate(
  expenditure_type_count=rowSums(.[expenditure_cols],na.rm=TRUE),
  expenditure_classification= ifelse( expenditure_type_count<=low_bound, low_bound_label,
                                             ifelse(expenditure_type_count>high_bound, high_bound_label, "other"))
  ) %>% 
  filter(expenditure_classification!="other") %>% 
  select(X_uuid,expenditure_type_count)
  
HH_yes_consent %>%
  mutate(
  expenditure_type_count=rowSums(.[expenditure_cols],na.rm=TRUE),
  expenditure_classification= ifelse( expenditure_type_count<=low_bound, low_bound_label,
                                             ifelse(expenditure_type_count>high_bound, high_bound_label, "other"))
  ) %>%   
  ggplot()+geom_histogram(aes(x=expenditure_type_count))

Expenditure_outliers%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Outlier Expenditures") %>% kable_styling(position = "center")


```

## Potential Contradictions
### Health coping and spending
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}

health_coping_to_check<-c("health_coping.ghealth_debt", "health_coping.pay_care","health_coping.comm_support")
HH[,health_coping_to_check]<- sapply(HH[,health_coping_to_check], function(x) ifelse(is.na(x),0,x))

health_coping_contradiction<-HH %>% 
  mutate(
    spent_on_medical=ifelse(rowSums(.[health_coping_to_check],na.rm=TRUE)>0,"spent_on_medical", "no_medical_spending"),
    spent_medical_coping_contradiction=ifelse(spent_on_medical=="spent_on_medical" &
                                                (exp_medical== "0_bdt"| exp_medical== NA), "contradiction",
                                              "no_contradiction")
    ) %>% 
  filter(spent_medical_coping_contradiction=="contradiction") %>% 
  select(X_uuid,enumerator_id, exp_medical, spent_on_medical,spent_medical_coping_contradiction) %>% 
  arrange(enumerator_id)

debt_health_contra2<-HH %>% 
  mutate(
    debt_health_contradiction=ifelse(health_coping.ghealth_debt== 1&debt_reason.pay_health_expenses== 0, "yes", "no")
  ) %>% 
  filter(debt_health_contradiction=="yes") %>% 
  select(X_uuid,enumerator_id,health_coping.ghealth_debt, debt_reason.pay_health_expenses,debt_health_contradiction)

debt_reason_columns<-HH %>% select(starts_with("debt_reason.")) %>% colnames()
any_debt_reason_and_no_debt_expenditures<-HH %>% 
  mutate(
    any_debt_reason= ifelse(rowSums(.[debt_reason_columns],na.rm=TRUE)>0,1,0),
    debt_expense_contradiction= ifelse(any_debt_reason==1 & exp_debt%in% c(NA,"0_bdt"),"yes","no")
  ) %>% 
  select(X_uuid,enumerator_id, any_debt_reason,exp_debt,debt_expense_contradiction) %>%
  filter(debt_expense_contradiction=="yes") %>% 
  arrange(enumerator_id)


health_coping_contradiction%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Health coping and spending") %>% kable_styling(position = "center")
debt_health_contra2%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Health Debt Issues") %>% kable_styling(position = "center")


any_debt_reason_and_no_debt_expenditures%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Any Debt Reason and No Expenditures") %>% kable_styling(position = "center")
```

### Rent Shelter Contradictions
```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE}
if(population=="Refugee"){ 
  rent_paid_q<-"shelter_paid"
}
if(population=="Host"){
  rent_paid_q<-"rent_host"  
}

rent_shelter_contradictions<-HH %>% 
  mutate(
    shelter_rent_contra= ifelse(exp_rent %in% c(NA,"0_bdt")& HH[[rent_paid_q]]=="yes", "yes", "no")
    ) %>% 
  select(X_uuid,enumerator_id, shelter_rent_contra) %>% 
  filter(shelter_rent_contra=="yes") %>% 
  arrange(enumerator_id)
rent_shelter_contradictions%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Shelter - Rent Issues") %>% kable_styling(position = "center")

shelter_exp_improvement_contradiction<-HH %>% 
  mutate(
    shelter_expenditures_contradiction=ifelse((exp_shelter_materials %in% c(NA,"0_bdt")==FALSE) & improvement.none==1, "yes", "no")
  ) %>% 
  select(X_uuid,enumerator_id, exp_shelter_materials, improvement.none,shelter_expenditures_contradiction) %>% 
  filter(shelter_expenditures_contradiction=="yes") 
shelter_exp_improvement_contradiction%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Shelter Expenditure- Improvement Contradiction") %>% kable_styling(position = "center")
```

## Durations

```{r eval=TRUE, echo=FALSE, results='asis', warning=FALSE, messages=FALSE,}

audit_yes<-Load_Audit(data=HH, path.to.zip = audit_zipfile,
           path.to.unzip = path_unzip,
           copy.zip = TRUE,
           path.to.copy.zip = copy_zip_to,
           delete.unzipped=TRUE
           )


# -	hh_coping_mechanism – enumerators spending less than 2 minutes here
# -	health_coping  --- enumerators spending less than a minute here
# -	FSC group (should appear all at once on the screen) – enumerators spending less than a minute here
# -	enough_water – enumerators spending less than 30 seconds here

dfl<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"informed_consent")& !is.na(event)) %>% 
    select(end) 
  start_question<-min(start_question$end)
  end_question<-d %>% filter(node==paste0(audit_node,"end_note")& !is.na(node)) %>% 
    select(start)
  end_question<-max(end_question$start)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl[[i]]<-data.frame(uuid=names(audit_yes)[i],duration_ms=duration_ms,durations_secs=duration_secs,duration_minutes= duration_minutes)
}

duration_df2<-do.call("rbind", dfl)

htdf<-HH_yes_consent %>%  
  left_join(duration_df2, by= c("X_uuid"="uuid"))

dfl<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"consent_received[1]/Food_security_Livelihood[1]/hh_coping_mechanism")& !is.na(event)) %>%
    select(start)
  start_question<-min(start_question$start)
  end_question<-d %>% filter(node==paste0(audit_node,"consent_received[1]/Food_security_Livelihood[1]/hh_coping_mechanism")& !is.na(node)) %>%
    select(end)
  end_question<-max(end_question$end)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl[[i]]<-data.frame(uuid=names(audit_yes)[i],duration_ms=duration_ms,durations_secs=duration_secs,duration_minutes= duration_minutes)
}

hh_coping_times<-do.call("rbind", dfl)
hh_coping_times$question<-"hh_coping_mechanism"


dfl<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"consent_received[1]/Health[1]/health_coping")& !is.na(event)) %>%
    select(start)
  start_question<-min(start_question$start)
  end_question<-d %>% filter(node==paste0(audit_node,"consent_received[1]/Health[1]/health_coping")& !is.na(node)) %>%
    select(end)
  end_question<-max(end_question$end)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl[[i]]<-data.frame(uuid=names(audit_yes)[i],duration_ms=duration_ms,durations_secs=duration_secs,duration_minutes= duration_minutes)
}

health_coping<-do.call("rbind", dfl)
health_coping$question<-"health_coping"

dfl<-list()
for (i in 1: length(audit_yes)){
  d<-audit_yes[[i]]
  start_question<- d %>% filter(node==paste0(audit_node,"consent_received[1]/WASH[1]/enough_water")& !is.na(event)) %>%
    select(start)
  start_question<-min(start_question$start)
  end_question<-d %>% filter(node==paste0(audit_node,"consent_received[1]/WASH[1]/enough_water")& !is.na(node)) %>%
    select(end)
  end_question<-max(end_question$end)
  duration_ms<-end_question-start_question
  duration_secs<-duration_ms/1000
  duration_minutes<- round(duration_secs/60,1)
  dfl[[i]]<-data.frame(uuid=names(audit_yes)[i],duration_ms=duration_ms,durations_secs=duration_secs,duration_minutes= duration_minutes)
}

enough_water<-do.call("rbind", dfl)
enough_water$question<-"enough_water"

question_specific_times<-do.call("rbind", list(hh_coping_times,health_coping, enough_water))

short_times_on_questions<-question_specific_times %>% 
  mutate(flag=if_else((duration_minutes<2 & question=="hh_coping_mechanism")|
                        (duration_minutes<1 & question== "health_coping")|
                        (duration_secs<30 & question=="enough_water"),1,0)) %>% 
  filter(flag==1) %>% 
  select(-flag, -duration_ms) %>% 
  arrange(uuid, duration_minutes)

short_times_on_questions_table<-short_times_on_questions %>% left_join(HH %>% select(X_uuid, enumerator_id, reported_date), by=c("uuid"="X_uuid")) %>% 
  select(uuid, enumerator_id, everything())


# short_times_on_questions_table%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Short Answer Times") %>% kable_styling(position = "center")





```

## DURATION STATISTICS
Statistics on survey duration are calculated from the audit file and are now correct.

The mean time for a completed questionaire so far is **`r mean(htdf$duration_minutes, na.rm=TRUE)`**.

The median time for a completed questionaire so far is **`r median(htdf$duration_minutes, na.rm=TRUE)`**.



```{r eval=TRUE, echo=FALSE, results='asis'}

# quick_surveys<-htdf[htdf$duration_minutes< mindur,]
quick_surveys<-htdf %>% filter(duration_minutes<mindur)


quick_survey_daily<-quick_surveys %>% group_by(reported_date, enumerator_id) %>% 
  select(reported_date, enumerator_id, X_uuid,duration_minutes, {strata}) %>% arrange(reported_date)

quick_survey_information<-data.frame(quick_surveys$enumerator_id,quick_surveys$X_uuid, quick_surveys$duration_minutes)

duration_by_enumerator <- htdf %>%
  mutate(zscore = scale(duration_minutes),
  zscoreLog = scale(log(duration_minutes))) %>%
  group_by(enumerator_id) %>%
  summarise(
  number_surveys=n(),  
  mean_duration = mean(duration_minutes, na.rm = TRUE),
  median_duration = median(duration_minutes, na.rm=TRUE)
  ) %>%
  ungroup %>%
  mutate(
  difference_from_mean = mean_duration - mean(htdf$duration_minutes,na.rm=TRUE),
  difference_from_median = median_duration - median(htdf$duration_minutes,na.rm=TRUE)
  )

# setnames(t,old=c("consent_received.res_18ormore_cont.above_18.num_mem", "consent_received.res_18ormore_cont.camp_satisfaction.water_cont_g.wat_containers_num"), new=c("num_mem","wat_containers_num"))
# list[dts,err]<-chk5b_duration_Xmin(t, consent, dates, c("enumerator_id", "X_uuid"), mindur, FALSE)
# HeaderYes<-dts
# setnames(HeaderYes,old=c("num_mem","wat_containers_num"), new=c("consent_received.res_18ormore_cont.above_18.num_mem", "consent_received.res_18ormore_cont.camp_satisfaction.water_cont_g.wat_containers_num"))
# kable(err, "latex", longtable = T, booktabs = T, linesep = "") %>% kable_styling(latex_options = c("repeat_header"), position = "center")

quick_survey_daily%>% kable( longtable = T, booktabs = T, linesep = "",caption= paste0("Enumerators That Completed a Full Survey In Less Than ",mindur, " minutes")) %>% kable_styling(position = "center")

# kable(quick_survey_daily, "latex", longtable = T, booktabs = T, linesep = "",
#       caption=paste0("Enumerators That Completed a Full Survey In Less Than ",mindur, " minutes")) %>% kable_styling(latex_options = c("repeat_header"), position = "center")

duration_by_enumerator%>% kable( longtable = T, booktabs = T, linesep = "",caption= "Duration Statistics By Enumerator (minutes)") %>% kable_styling(position = "center")


# kable(duration_by_enumerator, "latex", longtable = T, booktabs = T, linesep = "", caption= "Duration Statistics By Enumerator (minutes)") %>% kable_styling(latex_options = c("repeat_header"), position = "center")

```



```{r}

if(population=="Refugee"){
  HH_other<-HH %>% 
    select(-health_coping.home_treatment_other) %>% 
    filter_at(vars(ends_with("_other")), any_vars(!is.na(.))) %>% 
    select(X_uuid,enumerator_id,reported_date, ends_with("_other")) }

if(population=="Host"){
  HH_other<-HH %>% 
    filter_at(vars(ends_with("_other")), any_vars(!is.na(.))) %>% 
    select(X_uuid,enumerator_id,reported_date, ends_with("_other")) }
  

Indiv_more_data<-Indiv %>% left_join(HH_corrected_spatial_df %>%
                      select(X_uuid, enumerator_id, reported_date,{strata}), 
                    by=c("X_submission__uuid"="X_uuid"))

Indiv_other<-Indiv_more_data %>% 
  filter_at(vars(ends_with("_other")), any_vars(!is.na(.))) %>% 
  select(X_submission__uuid,enumerator_id,reported_date, ends_with("_other"))



Na_HH_table<-get_na_response_rates(data=HH_yes_consent)
Na_Indiv_table<-get_na_response_rates(data=Indiv_yes_consent)

if(write_output=="yes"){
  source("Functions/WriteOutputToCsvs.R")
}


```

